---
title: "Used Cars – Applied ML Project"
output: html_document
---

<!-- Load libraries -->
```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(here)
```

# About the Dataset (Summary)

The Used Car Price Prediction dataset contains 4,009 vehicle listings collected from the automotive marketplace cars.com.
Each row represents a unique car and includes nine key attributes relevant to pricing and vehicle characteristics.
Dataset is taken from Kaggle: https://www.kaggle.com/datasets/taeefnajib/used-car-price-prediction-dataset

The dataset provides information on:

**Brand and model** – manufacturer and specific vehicle model

**Model year ** – age of the car, influencing depreciation

**Mileage** – an indicator of usage and wear

**Fuel type** – e.g., gasoline, diesel, electric, hybrid

**Engine type** – performance and efficiency characteristics

**Transmission** – automatic or manual

**Exterior/interior colors** – aesthetic properties

**Accident history** – whether the car has previously been damaged

**Clean title** – legal/ownership status

**Price** – listed price of the vehicle

Overall, the dataset offers a structured overview of key features that influence used car valuation. It is well-suited for analytical tasks such as understanding pricing drivers, exploring consumer preferences, and building predictive models for vehicle prices.
# Raw data

We load the original CSV directly from the project data folder using `here()` so paths work regardless of the working directory.

```{r load-raw, message=FALSE}
raw_path <- here("data", "raw", "used_cars.csv")
cars_raw <- readr::read_csv(raw_path, show_col_types = FALSE)
```

Basic structure and summary statistics of the raw dataset:

```{r raw-summary}
glimpse(cars_raw)
```
